---
title: "Evaluation-of-filter-results_25x25"
author: "Kento Okuyama"
date: "2023-11-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## (very) Brief introduction

In this document, we evaluate the implementation of our frequentist implementation of the non-linear regime-switching state-space (RSSS) model estimation based on simulated data. Our parameter optimization consists of 300 iteration steps based on Adam. On top of that, we have 30 initialization of the starting parameter values.

In our implementation, our objective function **sumLik** is maximized based on the gradient vector and Adam. For evaluation purpose, we also have the score function **delta**. This is simply calculated as the summed squared error of the one-step-ahead (of the last observed time points) prediction of our intra-individual latent variables. Further, we also have **sensitivity** and **specificity** based on the one-step-ahead regime prediction results. 

For further details of the model formulation as well as theoretical foundation, please refer to my master thesis 'Forecasting in regime-switching models that emerge from filtering and machine learning'. In the following, we summarize our estimation results of 200 simulations (realizations of random variables). From now on, we focus exclusively on the 'best' result in each simulation study i.e., one that maximized our likelihood function among 30 initizalization * 300 iterations. 

```{r setting directory, echo=FALSE}
setwd('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300')
```

### N=25, T=25

```{r N_25_T_25, echo=FALSE}
N <- Nt <- 25

seed <- 1
filter_25x25_1 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 2
filter_25x25_2 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 3
filter_25x25_3 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 4
filter_25x25_4 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 5
filter_25x25_5 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 6
filter_25x25_6 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 7
filter_25x25_7 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 8
filter_25x25_8 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 9
filter_25x25_9 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 10
filter_25x25_10 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 11
filter_25x25_11 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))
```

```{r sumLik_25, echo=FALSE}
sumLik_25x25_1 <- filter_25x25_1$sumLik_best_NT
sumLik_25x25_2 <- filter_25x25_2$sumLik_best_NT
sumLik_25x25_3 <- filter_25x25_3$sumLik_best_NT
sumLik_25x25_4 <- filter_25x25_4$sumLik_best_NT
sumLik_25x25_5 <- filter_25x25_5$sumLik_best_NT
sumLik_25x25_6 <- filter_25x25_6$sumLik_best_NT
sumLik_25x25_7 <- filter_25x25_7$sumLik_best_NT
sumLik_25x25_8 <- filter_25x25_8$sumLik_best_NT
sumLik_25x25_9 <- filter_25x25_9$sumLik_best_NT
sumLik_25x25_10 <- filter_25x25_10$sumLik_best_NT
sumLik_25x25_11 <- filter_25x25_11$sumLik_best_NT
sumLik_25x25_group <- c(sumLik_25x25_1, sumLik_25x25_2, sumLik_25x25_3, sumLik_25x25_4, sumLik_25x25_5, sumLik_25x25_6, sumLik_25x25_7, sumLik_25x25_8, sumLik_25x25_9, sumLik_25x25_10, sumLik_25x25_11)
```

First, we check the distribution of the resulting **sumLik**

```{r sumLik_25x25_group}
hist(sumLik_25x25_group, breaks=15)
summary(sumLik_25x25_group)
```

and in log scale

```{r log_sumLik_25x25_group}
hist(log(sumLik_25x25_group), breaks=10)
summary(log(sumLik_25x25_group))
```

It seems like there are a few instances which has much higher **sumLik** than others.

```{r delta_25, echo=FALSE}
delta_25x25_1 <- filter_25x25_1$delta_N
delta_25x25_2 <- filter_25x25_2$delta_N
delta_25x25_3 <- filter_25x25_3$delta_N
delta_25x25_4 <- filter_25x25_4$delta_N
delta_25x25_5 <- filter_25x25_5$delta_N
delta_25x25_6 <- filter_25x25_6$delta_N
delta_25x25_7 <- filter_25x25_7$delta_N
delta_25x25_8 <- filter_25x25_8$delta_N
delta_25x25_9 <- filter_25x25_9$delta_N
delta_25x25_10 <- filter_25x25_10$delta_N
delta_25x25_11 <- filter_25x25_11$delta_N
delta_25x25_group <- c(delta_25x25_1, delta_25x25_2, delta_25x25_3, delta_25x25_4, delta_25x25_5, delta_25x25_6, delta_25x25_7, delta_25x25_8, delta_25x25_9, delta_25x25_10, delta_25x25_11)
```

Second, we check the distribution of the resulting **delta**
```{r delta_25x25_group}
hist(delta_25x25_group, breaks=10)
summary(delta_25x25_group)
```

and in log scale
```{r log_delta_25x25_group}
hist(log(delta_25x25_group), breaks=10)
summary(log(delta_25x25_group))
```

Please note that we prefer a smaller value as it is calculated based on the prediction error.

Next, we turn our attention to how the **sumLik** and **delta** correlate. Intuitively, we expect the negative correlation so that higher **sumLik** (maximized likelihood) relates to smaller **delta** (smaller prediction error).

```{r cor_sumLik_delta_25x25_group}
plot(sumLik_25x25_group, delta_25x25_group)
cor(sumLik_25x25_group, delta_25x25_group)
```

and in log scale
```{r cor_log_sumLik_log_delta_25x25_group}
plot(log(sumLik_25x25_group), log(delta_25x25_group))
cor(log(sumLik_25x25_group), log(delta_25x25_group))
```

Unfortunately, we see a positive correlation between **sumLik** and **delta**.

Then, we check the distribution of **sensitivity** and **specificity**.

```{r sensitivity_25, echo=FALSE}
sensitivity_25x25_1 <- filter_25x25_1$output_best$sensitivity
sensitivity_25x25_2 <- filter_25x25_2$output_best$sensitivity
sensitivity_25x25_3 <- filter_25x25_3$output_best$sensitivity
sensitivity_25x25_4 <- filter_25x25_4$output_best$sensitivity
sensitivity_25x25_5 <- filter_25x25_5$output_best$sensitivity
sensitivity_25x25_6 <- filter_25x25_6$output_best$sensitivity
sensitivity_25x25_7 <- filter_25x25_7$output_best$sensitivity
sensitivity_25x25_8 <- filter_25x25_8$output_best$sensitivity
sensitivity_25x25_9 <- filter_25x25_9$output_best$sensitivity
sensitivity_25x25_10 <- filter_25x25_10$output_best$sensitivity
sensitivity_25x25_11 <- filter_25x25_11$output_best$sensitivity
sensitivity_25x25_group <- c(sensitivity_25x25_1, sensitivity_25x25_2, sensitivity_25x25_3, sensitivity_25x25_4, sensitivity_25x25_5, sensitivity_25x25_6, sensitivity_25x25_7, sensitivity_25x25_8, sensitivity_25x25_9, sensitivity_25x25_10, sensitivity_25x25_11)
```

First for **sensitivity**
```{r sensitivity_25x25_group}
hist(sensitivity_25x25_group, breaks=15)
summary(sensitivity_25x25_group)
```

```{r output_best$specificity_25, echo=FALSE}
specificity_25x25_1 <- filter_25x25_1$output_best$specificity
specificity_25x25_2 <- filter_25x25_2$output_best$specificity
specificity_25x25_3 <- filter_25x25_3$output_best$specificity
specificity_25x25_4 <- filter_25x25_4$output_best$specificity
specificity_25x25_5 <- filter_25x25_5$output_best$specificity
specificity_25x25_6 <- filter_25x25_6$output_best$specificity
specificity_25x25_7 <- filter_25x25_7$output_best$specificity
specificity_25x25_8 <- filter_25x25_8$output_best$specificity
specificity_25x25_9 <- filter_25x25_9$output_best$specificity
specificity_25x25_10 <- filter_25x25_10$output_best$specificity
specificity_25x25_11 <- filter_25x25_11$output_best$specificity
specificity_25x25_group <- c(specificity_25x25_1, specificity_25x25_2, specificity_25x25_3, specificity_25x25_4, specificity_25x25_5, specificity_25x25_6, specificity_25x25_7, specificity_25x25_8, specificity_25x25_9, specificity_25x25_10, specificity_25x25_11)
```

And for **specificity**
```{r specificity_25x25_group}
hist(specificity_25x25_group, breaks=15)
summary(specificity_25x25_group)
```

We can also check the correlation between **sensitivity** and **specificity**.
```{r cor_sensitivity_specificity_25x25_group}
plot(sensitivity_25x25_group, specificity_25x25_group)
cor(sensitivity_25x25_group, specificity_25x25_group)
```

Finally we examine our parameter estimation.
```{r theta_25, echo=FALSE}
theta_25x25_1 <- filter_25x25_1$theta_best
theta_25x25_2 <- filter_25x25_2$theta_best
theta_25x25_3 <- filter_25x25_3$theta_best
theta_25x25_4 <- filter_25x25_4$theta_best
theta_25x25_5 <- filter_25x25_5$theta_best
theta_25x25_6 <- filter_25x25_6$theta_best
theta_25x25_7 <- filter_25x25_7$theta_best
theta_25x25_8 <- filter_25x25_8$theta_best
theta_25x25_9 <- filter_25x25_9$theta_best
theta_25x25_10 <- filter_25x25_10$theta_best
theta_25x25_11 <- filter_25x25_11$theta_best
theta_25x25_group <- rbind(theta_25x25_1, theta_25x25_2, theta_25x25_3, theta_25x25_4, theta_25x25_5, theta_25x25_6, theta_25x25_7, theta_25x25_8, theta_25x25_9, theta_25x25_10, theta_25x25_11)
colnames(theta_25x25_group) <- c('B11_1 (.2)', 'B11_2 (.3)', 'B12_1 (-.1)', 'B12_2 (-.2)', 'B21d_1 (.8)', 'B21d_2 (.8)', 'B22d_1 (.4)', 'B22d_2 (.4)', 'B31_1 (.1)', 'B31_2 (.1)', 'B32_1 (-.1)', 'B31_2 (-.1)', 'Lmdd_1 (1)', 'Lmdd_2 (0)', 'Lmdd_3 (.4)', 'Lmdd_4 (0)', 'Lmdd_5 (.8)', 'Lmdd_6 (0)', 'Lmdd_7 (0)', 'Lmdd_8 (1)', 'Lmdd_9 (0)', 'Lmdd_10 (.5)', 'Lmdd_11 (0)', 'Lmdd_12 (1.2)', 'Qd_1 (.2)', 'Qd_2 (.2)', 'Rd_1 (.3)', 'Rd_2 (.3)', 'Rd_3 (.3)', 'Rd_4 (.3)', 'Rd_5 (.3)', 'Rd_6 (.3)', 'gamma1 (3.5)', 'gamma2_1 (1)', 'gamma2_2 (1)')
```

The distribution of parameter estimation are shown below. True parameter values are in parenthesis.

```{r theta_25x25_group}
summary(theta_25x25_group)
```
