---
title: "Evaluation-of-filter-results_25x50"
author: "Kento Okuyama"
date: "2023-11-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## (very) Brief introduction

In this document, we evaluate the implementation of our frequentist implementation of the non-linear regime-switching state-space (RSSS) model estimation based on simulated data. Our parameter optimization consists of 300 iteration steps based on Adam. On top of that, we have 30 initialization of the starting parameter values.

In our implementation, our objective function **sumLik** is maximized based on the gradient vector and Adam. For evaluation purpose, we also have the score function **delta**. This is simply calculated as the summed squared error of the one-step-ahead (of the last observed time points) prediction of our intra-individual latent variables. Further, we also have **sensitivity** and **specificity** based on the one-step-ahead regime prediction results. 

For further details of the model formulation as well as theoretical foundation, please refer to my master thesis 'Forecasting in regime-switching models that emerge from filtering and machine learning'. In the following, we summarize our estimation results of 200 simulations (realizations of random variables). From now on, we focus exclusively on the 'best' result in each simulation study i.e., one that maximized our likelihood function among 30 initizalization * 300 iterations. 

```{r setting directory, echo=FALSE}
setwd('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300')
```

### N=25, T=50
```{r N_25_T_50, echo=FALSE}
N <- 25; Nt <- 50

seed <- 1
filter_25x50_1 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 2
filter_25x50_2 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 3
filter_25x50_3 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 4
filter_25x50_4 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 5
filter_25x50_5 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 6
filter_25x50_6 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 7
filter_25x50_7 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 8
filter_25x50_8 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 9
filter_25x50_9 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 10
filter_25x50_10 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 11
filter_25x50_11 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 12
filter_25x50_12 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 13
filter_25x50_13 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 14
filter_25x50_14 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 15
filter_25x50_15 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 16
filter_25x50_16 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 17
filter_25x50_17 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 18
filter_25x50_18 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 19
filter_25x50_19 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 20
filter_25x50_20 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 21
filter_25x50_21 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 22
filter_25x50_22 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 23
filter_25x50_23 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 24
filter_25x50_24 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 25
filter_25x50_25 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 26
filter_25x50_26 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))

seed <- 27
filter_25x50_27 <- readRDS(paste('C:/Users/kento/OneDrive - UT Cloud/Tuebingen/Research/Methods Center/Regime_Switching/Simulation/202309241300/output/filter__sim_', seed, '_N_', N, '_T_', Nt, '_O1_6_O2_3_L1_2.RDS', sep=''))
```

```{r sumLik_25x50, echo=FALSE}
sumLik_25x50_1 <- filter_25x50_1$sumLik_best_NT
sumLik_25x50_2 <- filter_25x50_2$sumLik_best_NT
sumLik_25x50_3 <- filter_25x50_3$sumLik_best_NT
sumLik_25x50_4 <- filter_25x50_4$sumLik_best_NT
sumLik_25x50_5 <- filter_25x50_5$sumLik_best_NT
sumLik_25x50_6 <- filter_25x50_6$sumLik_best_NT
sumLik_25x50_7 <- filter_25x50_7$sumLik_best_NT
sumLik_25x50_8 <- filter_25x50_8$sumLik_best_NT
sumLik_25x50_9 <- filter_25x50_9$sumLik_best_NT
sumLik_25x50_10 <- filter_25x50_10$sumLik_best_NT
sumLik_25x50_11 <- filter_25x50_11$sumLik_best_NT
sumLik_25x50_12 <- filter_25x50_12$sumLik_best_NT
sumLik_25x50_13 <- filter_25x50_13$sumLik_best_NT
sumLik_25x50_14 <- filter_25x50_14$sumLik_best_NT
sumLik_25x50_15 <- filter_25x50_15$sumLik_best_NT
sumLik_25x50_16 <- filter_25x50_16$sumLik_best_NT
sumLik_25x50_17 <- filter_25x50_17$sumLik_best_NT
sumLik_25x50_18 <- filter_25x50_18$sumLik_best_NT
sumLik_25x50_19 <- filter_25x50_19$sumLik_best_NT
sumLik_25x50_20 <- filter_25x50_20$sumLik_best_NT
sumLik_25x50_21 <- filter_25x50_21$sumLik_best_NT
sumLik_25x50_22 <- filter_25x50_22$sumLik_best_NT
sumLik_25x50_23 <- filter_25x50_23$sumLik_best_NT
sumLik_25x50_24 <- filter_25x50_24$sumLik_best_NT
sumLik_25x50_25 <- filter_25x50_25$sumLik_best_NT
sumLik_25x50_26 <- filter_25x50_26$sumLik_best_NT
sumLik_25x50_27 <- filter_25x50_27$sumLik_best_NT
sumLik_25x50_group <- c(sumLik_25x50_1, sumLik_25x50_2, sumLik_25x50_3, sumLik_25x50_4, sumLik_25x50_5, sumLik_25x50_6, sumLik_25x50_7, sumLik_25x50_8, sumLik_25x50_9, sumLik_25x50_10, sumLik_25x50_11, sumLik_25x50_12, sumLik_25x50_13, sumLik_25x50_14, sumLik_25x50_15, sumLik_25x50_16, sumLik_25x50_17, sumLik_25x50_18, sumLik_25x50_19, sumLik_25x50_20, sumLik_25x50_21, sumLik_25x50_22, sumLik_25x50_23, sumLik_25x50_24, sumLik_25x50_25, sumLik_25x50_26, sumLik_25x50_27)
```

First, we check the distribution of the resulting **sumLik**
```{r sumLik_25x50_group}
hist(sumLik_25x50_group, breaks=15)
summary(sumLik_25x50_group)
```

and in log scale
```{r log_sumLik_25x50_group}
hist(log(sumLik_25x50_group), breaks=10)
summary(log(sumLik_25x50_group))
```
It seems like there are a few instances which has much higher **sumLik** than others.

```{r delta_25x50, echo=FALSE}
delta_25x50_1 <- filter_25x50_1$delta_N
delta_25x50_2 <- filter_25x50_2$delta_N
delta_25x50_3 <- filter_25x50_3$delta_N
delta_25x50_4 <- filter_25x50_4$delta_N
delta_25x50_5 <- filter_25x50_5$delta_N
delta_25x50_6 <- filter_25x50_6$delta_N
delta_25x50_7 <- filter_25x50_7$delta_N
delta_25x50_8 <- filter_25x50_8$delta_N
delta_25x50_9 <- filter_25x50_9$delta_N
delta_25x50_10 <- filter_25x50_10$delta_N
delta_25x50_11 <- filter_25x50_11$delta_N
delta_25x50_12 <- filter_25x50_12$delta_N
delta_25x50_13 <- filter_25x50_13$delta_N
delta_25x50_14 <- filter_25x50_14$delta_N
delta_25x50_15 <- filter_25x50_15$delta_N
delta_25x50_16 <- filter_25x50_16$delta_N
delta_25x50_17 <- filter_25x50_17$delta_N
delta_25x50_18 <- filter_25x50_18$delta_N
delta_25x50_19 <- filter_25x50_19$delta_N
delta_25x50_20 <- filter_25x50_20$delta_N
delta_25x50_21 <- filter_25x50_21$delta_N
delta_25x50_22 <- filter_25x50_22$delta_N
delta_25x50_23 <- filter_25x50_23$delta_N
delta_25x50_24 <- filter_25x50_24$delta_N
delta_25x50_25 <- filter_25x50_25$delta_N
delta_25x50_26 <- filter_25x50_26$delta_N
delta_25x50_27 <- filter_25x50_27$delta_N
delta_25x50_group <- c(delta_25x50_1, delta_25x50_2, delta_25x50_3, delta_25x50_4, delta_25x50_5, delta_25x50_6, delta_25x50_7, delta_25x50_8, delta_25x50_9, delta_25x50_10, delta_25x50_11, delta_25x50_12, delta_25x50_13, delta_25x50_14, delta_25x50_15, delta_25x50_16, delta_25x50_17, delta_25x50_18, delta_25x50_19, delta_25x50_20, delta_25x50_21, delta_25x50_22, delta_25x50_23, delta_25x50_24, delta_25x50_25, delta_25x50_26, delta_25x50_27)
```

Second, we check the distribution of the resulting **delta**
```{r delta_25x50_group}
hist(delta_25x50_group, breaks=15)
summary(delta_25x50_group)
```

and in log scale
```{r log_delta_25x50_group}
hist(log(delta_25x50_group), breaks=10)
summary(log(delta_25x50_group))
```

Please note that we prefer a smaller value as it is calculated based on the prediction error.

Next, we turn our attention to how the **sumLik** and **delta** correlate. Intuitively, we expect the negative correlation so that higher **sumLik** (maximized likelihood) relates to smaller **delta** (smaller prediction error).

```{r cor_sumLik_delta_25x50_group}
plot(sumLik_25x50_group, delta_25x50_group)
cor(sumLik_25x50_group, delta_25x50_group)
```

and in log scale
```{r cor_log_sumLik_log_delta_25x50_group}
plot(log(sumLik_25x50_group), log(delta_25x50_group))
cor(log(sumLik_25x50_group), log(delta_25x50_group))
```

Unfortunately, we see a positive correlation between **sumLik** and **delta**.

Then, we check the distribution of **sensitivity** and **specificity**.

```{r sensitivity_25x50, echo=FALSE}
sensitivity_25x50_1 <- filter_25x50_1$output_best$sensitivity
sensitivity_25x50_2 <- filter_25x50_2$output_best$sensitivity
sensitivity_25x50_3 <- filter_25x50_3$output_best$sensitivity
sensitivity_25x50_4 <- filter_25x50_4$output_best$sensitivity
sensitivity_25x50_5 <- filter_25x50_5$output_best$sensitivity
sensitivity_25x50_6 <- filter_25x50_6$output_best$sensitivity
sensitivity_25x50_7 <- filter_25x50_7$output_best$sensitivity
sensitivity_25x50_8 <- filter_25x50_8$output_best$sensitivity
sensitivity_25x50_9 <- filter_25x50_9$output_best$sensitivity
sensitivity_25x50_10 <- filter_25x50_10$output_best$sensitivity
sensitivity_25x50_11 <- filter_25x50_11$output_best$sensitivity
sensitivity_25x50_12 <- filter_25x50_12$output_best$sensitivity
sensitivity_25x50_13 <- filter_25x50_13$output_best$sensitivity
sensitivity_25x50_14 <- filter_25x50_14$output_best$sensitivity
sensitivity_25x50_15 <- filter_25x50_15$output_best$sensitivity
sensitivity_25x50_16 <- filter_25x50_16$output_best$sensitivity
sensitivity_25x50_17 <- filter_25x50_17$output_best$sensitivity
sensitivity_25x50_18 <- filter_25x50_18$output_best$sensitivity
sensitivity_25x50_19 <- filter_25x50_19$output_best$sensitivity
sensitivity_25x50_20 <- filter_25x50_20$output_best$sensitivity
sensitivity_25x50_21 <- filter_25x50_21$output_best$sensitivity
sensitivity_25x50_22 <- filter_25x50_22$output_best$sensitivity
sensitivity_25x50_23 <- filter_25x50_23$output_best$sensitivity
sensitivity_25x50_24 <- filter_25x50_24$output_best$sensitivity
sensitivity_25x50_25 <- filter_25x50_25$output_best$sensitivity
sensitivity_25x50_26 <- filter_25x50_26$output_best$sensitivity
sensitivity_25x50_27 <- filter_25x50_27$output_best$sensitivity
sensitivity_25x50_group <- c(sensitivity_25x50_1, sensitivity_25x50_2, sensitivity_25x50_3, sensitivity_25x50_4, sensitivity_25x50_5, sensitivity_25x50_6, sensitivity_25x50_7, sensitivity_25x50_8, sensitivity_25x50_9, sensitivity_25x50_10, sensitivity_25x50_11, sensitivity_25x50_12, sensitivity_25x50_13, sensitivity_25x50_14, sensitivity_25x50_15, sensitivity_25x50_16, sensitivity_25x50_17, sensitivity_25x50_18, sensitivity_25x50_19, sensitivity_25x50_20, sensitivity_25x50_21, sensitivity_25x50_22, sensitivity_25x50_23, sensitivity_25x50_24, sensitivity_25x50_25, sensitivity_25x50_26, sensitivity_25x50_27)
```

First for **sensitivity**
```{r sensitivity_25x50_group}
hist(sensitivity_25x50_group, breaks=10)
summary(sensitivity_25x50_group)
```

```{r output_best$specificity_25x50, echo=FALSE}
specificity_25x50_1 <- filter_25x50_1$output_best$specificity
specificity_25x50_2 <- filter_25x50_2$output_best$specificity
specificity_25x50_3 <- filter_25x50_3$output_best$specificity
specificity_25x50_4 <- filter_25x50_4$output_best$specificity
specificity_25x50_5 <- filter_25x50_5$output_best$specificity
specificity_25x50_6 <- filter_25x50_6$output_best$specificity
specificity_25x50_7 <- filter_25x50_7$output_best$specificity
specificity_25x50_8 <- filter_25x50_8$output_best$specificity
specificity_25x50_9 <- filter_25x50_9$output_best$specificity
specificity_25x50_10 <- filter_25x50_10$output_best$specificity
specificity_25x50_11 <- filter_25x50_11$output_best$specificity
specificity_25x50_12 <- filter_25x50_12$output_best$specificity
specificity_25x50_13 <- filter_25x50_13$output_best$specificity
specificity_25x50_14 <- filter_25x50_14$output_best$specificity
specificity_25x50_15 <- filter_25x50_15$output_best$specificity
specificity_25x50_16 <- filter_25x50_16$output_best$specificity
specificity_25x50_17 <- filter_25x50_17$output_best$specificity
specificity_25x50_18 <- filter_25x50_18$output_best$specificity
specificity_25x50_19 <- filter_25x50_19$output_best$specificity
specificity_25x50_20 <- filter_25x50_20$output_best$specificity
specificity_25x50_21 <- filter_25x50_21$output_best$specificity
specificity_25x50_22 <- filter_25x50_22$output_best$specificity
specificity_25x50_23 <- filter_25x50_23$output_best$specificity
specificity_25x50_24 <- filter_25x50_24$output_best$specificity
specificity_25x50_25 <- filter_25x50_25$output_best$specificity
specificity_25x50_26 <- filter_25x50_26$output_best$specificity
specificity_25x50_27 <- filter_25x50_27$output_best$specificity
specificity_25x50_group <- c(specificity_25x50_1, specificity_25x50_2, specificity_25x50_3, specificity_25x50_4, specificity_25x50_5, specificity_25x50_6, specificity_25x50_7, specificity_25x50_8, specificity_25x50_9, specificity_25x50_10, specificity_25x50_11, specificity_25x50_12, specificity_25x50_13, specificity_25x50_14, specificity_25x50_15, specificity_25x50_16, specificity_25x50_17, specificity_25x50_18, specificity_25x50_19, specificity_25x50_20, specificity_25x50_21, specificity_25x50_22, specificity_25x50_23, specificity_25x50_24, specificity_25x50_25, specificity_25x50_26, specificity_25x50_27)
```

And for **specificity**
```{r specificity_25x50_group}
hist(specificity_25x50_group, breaks=15)
summary(specificity_25x50_group)
```

We can also check the correlation between **sensitivity** and **specificity**.
```{r cor_sensitivity_specificity_25x50_group}
plot(sensitivity_25x50_group, specificity_25x50_group)
cor(sensitivity_25x50_group, specificity_25x50_group)
```

Finally we examine our parameter estimation.
```{r theta_25x50, echo=FALSE}
theta_25x50_1 <- filter_25x50_1$theta_best
theta_25x50_2 <- filter_25x50_2$theta_best
theta_25x50_3 <- filter_25x50_3$theta_best
theta_25x50_4 <- filter_25x50_4$theta_best
theta_25x50_5 <- filter_25x50_5$theta_best
theta_25x50_6 <- filter_25x50_6$theta_best
theta_25x50_7 <- filter_25x50_7$theta_best
theta_25x50_8 <- filter_25x50_8$theta_best
theta_25x50_9 <- filter_25x50_9$theta_best
theta_25x50_10 <- filter_25x50_10$theta_best
theta_25x50_11 <- filter_25x50_11$theta_best
theta_25x50_12 <- filter_25x50_12$theta_best
theta_25x50_13 <- filter_25x50_13$theta_best
theta_25x50_14 <- filter_25x50_14$theta_best
theta_25x50_15 <- filter_25x50_15$theta_best
theta_25x50_16 <- filter_25x50_16$theta_best
theta_25x50_17 <- filter_25x50_17$theta_best
theta_25x50_18 <- filter_25x50_18$theta_best
theta_25x50_19 <- filter_25x50_19$theta_best
theta_25x50_20 <- filter_25x50_20$theta_best
theta_25x50_21 <- filter_25x50_21$theta_best
theta_25x50_22 <- filter_25x50_22$theta_best
theta_25x50_23 <- filter_25x50_23$theta_best
theta_25x50_24 <- filter_25x50_24$theta_best
theta_25x50_25 <- filter_25x50_25$theta_best
theta_25x50_26 <- filter_25x50_26$theta_best
theta_25x50_27 <- filter_25x50_27$theta_best
theta_25x50_group <- rbind(theta_25x50_1, theta_25x50_2, theta_25x50_3, theta_25x50_4, theta_25x50_5, theta_25x50_6, theta_25x50_7, theta_25x50_8, theta_25x50_9, theta_25x50_10, theta_25x50_11, theta_25x50_12, theta_25x50_13, theta_25x50_14, theta_25x50_15, theta_25x50_16, theta_25x50_17, theta_25x50_18, theta_25x50_19, theta_25x50_20, theta_25x50_21, theta_25x50_22, theta_25x50_23, theta_25x50_24, theta_25x50_25, theta_25x50_26, theta_25x50_27)
colnames(theta_25x50_group) <- c('B11_1 (.2)', 'B11_2 (.3)', 'B12_1 (-.1)', 'B12_2 (-.2)', 'B21d_1 (.8)', 'B21d_2 (.8)', 'B22d_1 (.4)', 'B22d_2 (.4)', 'B31_1 (.1)', 'B31_2 (.1)', 'B32_1 (-.1)', 'B31_2 (-.1)', 'Lmdd_1 (1)', 'Lmdd_2 (0)', 'Lmdd_3 (.4)', 'Lmdd_4 (0)', 'Lmdd_5 (.8)', 'Lmdd_6 (0)', 'Lmdd_7 (0)', 'Lmdd_8 (1)', 'Lmdd_9 (0)', 'Lmdd_10 (.5)', 'Lmdd_11 (0)', 'Lmdd_12 (1.2)', 'Qd_1 (.2)', 'Qd_2 (.2)', 'Rd_1 (.3)', 'Rd_2 (.3)', 'Rd_3 (.3)', 'Rd_4 (.3)', 'Rd_5 (.3)', 'Rd_6 (.3)', 'gamma1 (3.5)', 'gamma2_1 (1)', 'gamma2_2 (1)')
```

The distribution of parameter estimation are shown below. True parameter values are in parenthesis.

```{r theta_25x50_group}
summary(theta_25x50_group)
```
